### 2020-11-17 paper/draft1.tex
Update draft1.tex

Similar to work in [ELF Citation], we will focus on using the \textbf{proper scoring rule}, the \textbf{quadratic scoring rule} in our forecaster selection mechanism.\\

@@

\subsection{Truthfulness}
Note: The following analysis is inspired by and follows the work done in [ELF Citation].\\\\
For a single event with true probability $\theta$, every forecaster will either win 1 or 0 events. The probability that their final score is 1 will just be their expected score for the single event. Therefore, to maximize their final score, each forecaster must maximize their expected score for the single event. Their score is just $\E_{x \sim \theta}(R_q(y_i, x)) = \E_{x \sim \theta}(1 - (y_i - x)^2)$. This is maximized when $y_i = \theta$, so the mechanism is truthful. (what theorem 4 does) We can also see this directly be noting that $R_q$ is a strictly proper scoring rule, so its expectation is maximized when $y_i = \theta$.

>>>>

Similar to work in \cite{elf}, we will focus on using the \textbf{proper scoring rule}, the \textbf{quadratic scoring rule} in our forecaster selection mechanism.\\

@@

\subsection{Truthfulness}
Note: The following analysis is inspired by and follows the work done in \cite{elf}.\\\\
For a single event with true probability $\theta$, every forecaster will either win 1 or 0 events. The probability that their final score is 1 will just be their expected score for the single event. Therefore, to maximize their final score, each forecaster must maximize their expected score for the single event. Their score is just $\E_{x \sim \theta}(R_q(y_i, x)) = \E_{x \sim \theta}(1 - (y_i - x)^2)$. This is maximized when $y_i = \theta$, so the mechanism is truthful. (what theorem 4 does) We can also see this directly be noting that $R_q$ is a strictly proper scoring rule, so its expectation is maximized when $y_i = \theta$.
